Supp mat: time series paper

### 2017-05-11 writing/supp_mat_draft.Rmd
updated supp mat with outline and r code

---
title: 'Supp mat: time series paper'
author: "Easton R. White"
date: "February 1, 2017"
output: html_document
---

This is where I will build a supplementary material file

## Example of subsamling and power calculations

@@

```{r, echo=F}
# show an example
```

@@

# Supplementary material

```{r,echo=F}
# Example of using population growth rate instead of power
setwd("~/Desktop/Research/time-series-project")
source("scripts/calculate_geometric_growth.R")

@@

aaa=calculate_average_geometric_growth(pop$popvalue)
plot(rowMeans(aaa,na.rm=T),cex.axis=1.2,pch=16,ylab='',xlab='',las=1)
mtext(text = 'years sampled',1,line=3,cex=1.4)
mtext(text = 'population growth rate',2,line=3.7,cex=1.4)
```

>>>>

---
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: true
    citation_package: natbib
fontsize: 12pt
geometry: margin=0.75in
bibliography: White_bib.bib
header-includes: 
    \usepackage{float}
    \renewcommand{\thepage}{S\arabic{page}} 
    \renewcommand{\thesection}{S\arabic{section}}  
    \renewcommand{\thetable}{S\arabic{table}}  
    \renewcommand{\thefigure}{S\arabic{figure}}
---

\vspace{2cm}

\begin{center}
 \textbf{Supplementary Material: Article title here}

Authors: Easton R. White$^{1*}$
\vspace{3 mm}

Address: \\ \emph{$^1$ Center for Population Biology, University of California-Davis, Davis, California 95616 USA}

*Corresponding author: eawhite@ucdavis.edu

Dec XX, 2016
 \end{center}

\vspace{2cm}

This supplementary material includes:

1. Mathematical description of our model
2. Inverse pattern-orientated estimation procedure

Code for all the figures and tables can be found on [Github](https://github.com/erwhite1).

\vspace{2cm}

## Detailed example of subsampling and power calculations

@@

```{r, echo=F}
# show an example of subsampling and power calculation routines
```

@@

### Growth rate calculations

```{r, echo=F, fig.cap='duh\\label{fig:growth_rate}'}
#Example of using population growth rate instead of power
setwd("/Users/eastonwhite/Desktop/Research/time-series-project")
source("scripts/calculate_geometric_growth.R")
load('cleaned-data/pop_info_example_goodNAs.Rdata')

@@

  source('scripts/create_subsamples.R')
  aaa=calculate_average_geometric_growth(pop$popvalue)
  plot(rowMeans(aaa,na.rm=T),cex.axis=1.2,pch=16,ylab='',xlab='',las=1)
    mtext(text = 'years sampled',1,line=3,cex=1.4)
    mtext(text = 'population growth rate',2,line=3.7,cex=1.4)
```

### Using Generalized additive model to identify significant trends

TEXT HERE ON IDEA

```{r,echo=F,fig.cap='results here from GAM.\\label{fig:gam_example}'}
# show gam example side-by-side plot
```

```{r,echo=F,fig.cap='results here from GAM.\\label{fig:gam_result}'}
# show gam results for minimium time required
```

### References

### 2017-05-11 writing/supp_mat_draft.tex
updated supp mat with outline and r code

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{plainnat}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

Authors: Easton R. White$^{1*}$ , John D. Nagy$^{2,3}$, and Andrew T. Smith$^4$ 
\vspace{3 mm}

Address: \\ \emph{$^1$ Center for Population Biology, University of California-Davis, Davis, California 95616 USA; \\ $^2$ Department of Life Science, Scottsdale Community College, Scottsdale, Arizona 85253 USA; \\ $^3$ School of Mathematical and Statistical Sciences, Arizona State University, Tempe, Arizona 85287 USA; \\ $^4$ School of Life Sciences, Arizona State University, Tempe, Arizona 85287 USA}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Mathematical description of our model
\item
  Inverse pattern-orientated estimation procedure
\item
  Effects of spatial structure and patch heterogeneity
\item
  Mainland-Island effect
\item
  Invasion from southern area of study site
\item
  Parameter sensitivity
\item
  Effect of unsampled patches
\item
  Long term dynamics
\item
  Individual patch dynamics over time
\end{enumerate}

@@

\subsection{Example of subsamling and power
calculations}\label{example-of-subsamling-and-power-calculations}

@@

\section{\texorpdfstring{Supplementary material
\ref{fig:growth_rate}}{Supplementary material }}\label{supplementary-material}

@@

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{plainnat}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

Authors: Easton R. White$^{1*}$
\vspace{3 mm}

Address: \\ \emph{$^1$ Center for Population Biology, University of California-Davis, Davis, California 95616 USA}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Mathematical description of our model
\item
  Inverse pattern-orientated estimation procedure
\end{enumerate}

@@

\subsection{Detailed example of subsampling and power
calculations}\label{detailed-example-of-subsampling-and-power-calculations}

@@

\subsubsection{Growth rate calculations}\label{growth-rate-calculations}

\begin{verbatim}
## Loading required package: plyr
\end{verbatim}

@@

\subsubsection{Using Generalized additive model to identify significant
trends}\label{using-generalized-additive-model-to-identify-significant-trends}

TEXT HERE ON IDEA

\subsubsection{References}\label{references}
